### 2021-04-27 docs/manuscript/PLOS-MSc-Thesis.tex
Mention Cotterell and Sharpe work in introduction

>>>>

Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity \cite{Cotterell2010}.
